---
title: "Exercises for Dependent Effect Sizes"
author: "Megha Joshi"
date: "4/12/2022"
output: 
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data

Below I am loading the Tanner-Smith and Lipsey (2015) data that I went over in the presentation. 

```{r, warning = F, message = F}
library(tidyverse)

load("tsl_dat_20.RData")

glimpse(tsl_dat)
```

# Questions

1. Calculate the number of studies and calculate the number of effect sizes within each study?

2. What is dependence? How can it occur in a meta-analytic dataset?

3. Calculate the average effect of brief alcohol intervention not accounting for any moderators using `robu()` from `robumeta`. 

4. Run a meta-regression model with just `dv` (dependent variable measure) as a moderator. Estimate the effect of dependent variable of effect of brief alcohol interventions.

5. In the prior analyses, what kind of test and corrections does `robumeta` implement by default? What would be the consequence if we ignored the dependent structure of the meta-analytic data?

6. Using the meta-regression model you estimated in question 4, run a multiple-contrast hypothesis test to examine if effects differ according different dependent variable measures using the `Wald_test()` function from `clubSandwich` package. Use CR2 correction and HTZ test. 

7. According to the results of my simulation studies, what could potentially be the problem in the result of the multiple-contrast test you just conducted? Why would practitioners and policy-makers care about this problem?

8. Run multiple-contrast hypothesis test using `Wald_test_cwb()` from `wildmeta`. Compare the p-values that you calculated from from `wildmeta` and `clubSandwich`.
